When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2017-11-10 paper/paper.tex
Define search nodes
Better punctuation

Our experiments will primarily measure the number of recursive calls (guessed assignments) made, not
runtimes. We are not aiming to give a simple comparison of absolute performance between solvers;
rather, we are looking for solver-independent patterns of difficulty. All experiments use a timeout
of 1,000 seconds, which is enough for the Glasgow solver to solve nearly all instances (whose orders
were selected with this timeout in mind), although we may slightly overestimate the proportion of
unsatisfiable instances for extremely sparse or dense pattern graphs. The LAD, VF2, and VF3 solvers
experienced many more failures with this timeout, so our picture of just how hard the hardest
instances are with these solvers is less detailed.

@@

The line plots mean search effort using the Glasgow solver: for sparse patterns, the problem is
trivial, for dense patterns proving unsatisfiability is not particularly difficult, and we see a
complexity peak around the point where half the instances are satisfiable.  We also plot the search
cost of individual instances, as points. The behaviour we observe looks remarkably similar to random
3SAT problems---compare, for example, Figure~1 of \citet{DBLP:journals/cacm/Leyton-BrownHHX14}. In
particular, satisfiable instances tend to be easier, but show greater variation than unsatisfiable
instances, and there are exceptionally hard satisfiable instances \citep{DBLP:conf/cp/SmithG97}.

>>>>

Our experiments will primarily measure the number of \emph{search nodes} (that is, the number of
recursive calls made, or the number of guessed assignments), not runtimes. We are not aiming to give
a simple comparison of absolute performance between solvers; rather, we are looking for
solver-independent patterns of difficulty. All experiments use a timeout of 1,000 seconds, which is
enough for the Glasgow solver to solve nearly all instances (whose orders were selected with this
timeout in mind), although we may slightly overestimate the proportion of unsatisfiable instances
for extremely sparse or dense pattern graphs. The LAD, VF2, and VF3 solvers experienced many more
failures with this timeout, so our picture of just how hard the hardest instances are with these
solvers is less detailed.

@@

The line plots mean search effort using the Glasgow solver: for sparse patterns, the problem is
trivial; for dense patterns, proving unsatisfiability is not particularly difficult; and we see a
complexity peak around the point where half the instances are satisfiable.  We also plot the search
cost of individual instances, as points. The behaviour we observe looks remarkably similar to random
3SAT problems---compare, for example, Figure~1 of \citet{DBLP:journals/cacm/Leyton-BrownHHX14}. In
particular, satisfiable instances tend to be easier, but show greater variation than unsatisfiable
instances, and there are exceptionally hard satisfiable instances \citep{DBLP:conf/cp/SmithG97}.
